The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-23 paper/ms.tex
update

There are three clear effects on the line's morphology as the
rotational velocity increases. First, the line
broadens; second, the double peaks reduce their intensity; and third,
the intensity at the line center rises. The last two effects merge to give the
impression that the double peaks are merger into one at high rotational
velocities, a result that is evident for the homogeneously distributed
sources as shown in the dashed lines of Figure \ref{fig:differentvelocities}.

We use the full width at half maximum (FWHM) to quantify the line
broadening. For this we measure the width by finding
the closest points to the half maximum in our histogram numerically. 
 Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
with rotational velocity both for the central an homogeneous source
distributions.  We parametrize the dependency of the line width with
$V_{\rm max}$ as
\begin{equation}
 {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where FWHM$_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.89 \pm 0.04$ and $\lambda_{\rm h}=
1.98\pm 0.06$ respectively.

>>>>

There are three clear effects on the line's morphology as the
rotational velocity increases. First, the line
broadens; second, the double peaks reduce their intensity; and third,
the intensity at the line center rises, this effects are present for 
all the viewing angles. The last two effects merge to give the
impression that the double peaks are merger into one at high rotational
velocities, a result that is evident for the homogeneously distributed
sources as shown in the dashed lines of Figure \ref{fig:differentvelocities}.

We use the full width at half maximum (FWHM) to quantify the line
broadening. For this we measure the width by interpolating dots in 
our spectra this would produce a continuous spectra which makes easier
to find the half maximum in our histogram numerically, just finding the 
values of the width at the half maximum.

 Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
with rotational velocity both for the central (continuous lines) an 
homogeneous (dashed lines) sources, for $\theta=\pi/2$.
 We parametrize the dependency of the line width with
$V_{\rm max}$ as
\begin{equation}
 {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where FWHM$_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.89 \pm 0.04$ and $\lambda_{\rm h}=
1.98\pm 0.06$ respectively.
